Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-05-01 paper/paper.tex

\subsubsection{Image Acquisition}
While the automobile detection subsystem correctly identifies when a vehicle enters the lot, the image acquisition subsystem is responsible for determining when to capture a picture of that car in order to optimize the quality of the license plate image. The timing difference between when the Raspberry Pi receives the signal from the Arduino Fio and when the image is captured is set to 500 milliseconds so as to allow the car to completely pass the Arduino Fio and enter the capture area. Only one picture is taken of each car so that capture time and power consumption on the Raspberry Pi are limited. This allows for more resources to be allocated towards the process of image processing.

\subsubsection{Image Processing}
Once the image is captured, the Raspberry Pi will then focus on detecting the license plate in the image and cropping the image to only include the license plate. This will be done in order to minimize the size of the transmission and the power required for that transmission. In order to detect the location of the license plate within the larger image, a detection algorithm needs to be applied.

The location of the license plates will be detected on the acquisition Raspberry Pi using the OpenCV (Open Source Computer Vision Library) API \cite{openCV}, which provides many different algorithms that can be used for image detection and shape recognition. This particular API was chosen for both its ease of use and widespread cross-compatibility; it has interfaces for development in C, C++, Python, Java, and MATLAB, and supports all major operating systems (including distributions of Linux such as Raspbian). Because OpenCV is used across the industry for image processing, we are confident that it will meet our needs.

Once the OpenCV software has detected the license plate, the image will then be cropped as needed until all that remains in the image is the license plate from the car that is entering the lot. That image will then be sent to the central base station via an XBee radio transmission.

\subsection{Central Base Station}
{\color{red}\textbf{NOT COMPLETE}}
\begin{figure}
\begin{center}
\includegraphics[width=4.5in]{basestation}
\end{center}
\caption{Central Base Station Hardware}
\label{fig:basestation}
\end{figure}
The central base station is the point of contact between the sensor network and the server. The data gathered by the Arduino Fio and Raspberry Pi sensors are routed to the base station via XBee radios. The base station, which is itself a Raspberry Pi, forwards the data to the ACMx server using HTTP requests. Forwarding data is the main function of the base station. The base station runs the Raspbian operating system \cite{raspbian}, a lightweight version of Linux. Raspbian is optimized for the Raspberry Pi, so writing Python scripts that take care of forwarding the data via HTTP to the server was simple. The more difficult task was writing code to allow the base station Raspberry Pi to interface with the XBee radio, and listen for packets coming from the XBee attached to the Arduino Fio. The Python code that runs on the base station Raspberry Pi is listed in Appendix 2.

\subsection{Server Processing}
{\color{red}\textbf{NOT COMPLETE}}
Once an image has been captured by an Acquisition Raspberry Pi it is transmitted via the XBee radio to the base station Raspberry Pi, where it is uploaded to the server via an Ethernet connection. The REST route to which the image is posted serves several purposes. First, it authenticates the sender by checking for a username and password. The script then timestamps the image and saves it to a directory on the server not directly accessible from the web. Lastly, the script calls a function to invoke two different automatic license plate recognition (ALPR) programs and stores the resulting character extractions to a MySQL database.

>>>>

\subsubsection{Image Acquisition}
While the automobile detection subsystem correctly identifies when a vehicle enters the lot, the image acquisition subsystem is responsible for determining when to capture a picture of that car in order to optimize the quality of the license plate image. The timing difference between when the Raspberry Pi receives the signal from the Arduino Fio and when the image is captured is set to 500 milliseconds so as to allow the car to completely pass the Arduino Fio and enter the capture area. Only one picture is taken of each car so that capture time and power consumption on the Raspberry Pi are limited. This frees up more resources to be allocated towards the process of image processing.

\subsubsection{Image Processing}
Once an image is captured, the Raspberry Pi creates a subprocess which processes the captured image. The image is processed using the OpenCV (Open Source Computer Vision Library) API \cite{openCV}. This API provides many different algorithms that can be used for image detection and shape recognition. It was chosen for both its ease of use and widespread cross-compatibility; it has interfaces for development in C, C++, Python, Java, and MATLAB, and supports all major operating systems (including distributions of Linux such as Raspbian).

When processing the image, two factors are taken into consideration:
\begin{enumerate}
\item File Size and
\item License Plate Quality
\end{enumerate}
The file size is reduced as much as possible in order to expedite the file transfer process from the Acquisition Raspberry Pi. The second factor, license plate quality, is considered because the image must be readable by the Optical Character Recognition (OCR) software used on the server. Several different methods of processing the images using OpenCV were attempted, including but not limited to:
\begin{enumerate}
\item Contour Mapping,
\item Image Cropping,
\item Image Resizing and Compression, and
\item Color Manipulation
\end{enumerate}

Two datasets are analyzed on how they ran through the OCR software (section 4.2). These two datasets, "cropped images" and "compressed images" had different methods of processing applied. "Cropped images" is a set of images that were greedily cropped to eliminate space at the top and bottom of the picture around the car and were converted to grayscale images. "Compressed images" is a set of images that had various amounts of compression applied to them as well as different color filters.

Once the software has processed the image is sent to the ACMx server via a wi-fi connection.

\subsection{Central Base Station}
{\color{red}\textbf{NOT COMPLETE}}
\begin{figure}
\begin{center}
\includegraphics[width=4.5in]{basestation}
\end{center}
\caption{Central Base Station Hardware}
\label{fig:basestation}
\end{figure}

The central base station is the point of contact between the sensor network and the server. The data gathered by the Arduino Fio and Raspberry Pi sensors are routed to the base station via XBee radios. The base station, which is itself a Raspberry Pi, forwards the data to the ACMx server using HTTP requests. Forwarding data is the main function of the base station. The base station runs the Raspbian operating system \cite{raspbian}, a lightweight version of Linux. Raspbian is optimized for the Raspberry Pi, so writing Python scripts that take care of forwarding the data via HTTP to the server was simple.

\subsection{Server Processing}
Once an image has been captured by an Acquisition Raspberry Pi it is transmitted via the XBee radio to the base station Raspberry Pi where it is uploaded online via an Ethernet connection. The REST route that the image is posted serves several purposes. First, it authenticates the sender by checking for a username and password. The script then timestamps the image and saves it to a directory on the server not directly accessible from the web. Lastly, the script calls a function to invoke two different automatic license plate recognition (ALPR) programs and store the resulting character extraction to a MySQL database.
